Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2020-02-05 Tex/Old text/chapters/chapterverification.tex
thesis update

In the houses that use a $975$ W PV system (house $1$, house $2$, house $3$, and house $4$), ESBMC reached an error in any of the four houses and the execution time took less than $01$ s. Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for house $1$, with the FAIL identified. The author highlighted the result, which shows that the design flaw was found (SAT result or SUCCESS) within the bound $k$ of $100$, when a expected PV panels total power of $1,636.76$ W is expected and the sized system has only $975$ W. This flaw is related to Eq.~\eqref{eq:Pminpanel}.

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{homersimuh2no.png}
\centering
\caption{HOMER simulation screen presented for house 2 with no feasible solution found.}
\label{fig:homersimuh2no}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{homersimuh2yes.png}
\centering
\caption{HOMER simulation screen presented for house 2 with viable solution.}
\label{fig:homersimuh2yes}
\end{figure}

@@

In order to evaluate which validation is correct, it was necessary to consult the access interviews conducted with the residents of the deployed systems. From July $2018$ to March $2019$, surveys were applied to the residents on a monthly basis and data was collected from a local monitoring system: energy interruptions of the PV systems were not reported every month.

However, even when only one interruption is reported in a month, this represents around $3.33$\% interruption for the entire period ($1/30$), which indicates $96.97$\% of availability of the PV system ($96.67\% = 100\%-3.33\%$), and in accordance to what was described in Section~\ref{sec:availability}, the type of electrical load of the houses is not critical; this situation is considered an energy interruption, not a system flaw, further affirming EQ1. Therefore, the proposed approach using automated verification provides the correct evaluation of the PV system, thus answering EQ2.

All tools indicated flaws in house $5$ (automated verification or simulation); however, only the automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering EQ2.

In order to validate the possible flaw identified by the automated verification in house $5$, the owner of the $1,300$ W system was interviewed. From this it became clear that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double-checked against the monitoring system of the charge controller, which showed that the maximum power or surge power was not exceeded, thus affirming EQ1; this behavior is to be expected since the system was purchased as an off-the-shelf solution and not as a customized design for the house's electrical charges.

@@

This Chapter presented a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
Nevertheless, it also identified five threats to the validity of the results that bear further assessment.

@@

\textit{Simulation Tool:} Only HOMER Pro was used. The inclusion of other specialized simulation tools or even a general simulation tool that uses the same mathematical model adopted by the automated verification could change the comparison.

\textit{Temperature and Solar Irradiance Data}: Information relating to the temperature and solar irradiance of each case study, whether it is using simulation or formal verification, comes from databases available online~\cite{Temperature, Irradiance}. However, in view of the fact that riverside communities do not have weather stations, the data used in the present study comes from the municipality closest (Manaus in all the case studies), where stations regularly collect the data. Nevertheless, accuracy recommends the use of weather stations in each location.

@@

Based on the fact that all case studies were deployed in the field, with regular visits to conduct interviews with the residents, and with monitoring systems in some of the houses (house $1$, house $2$, house $3$, and house $4$), it was possible to compare the computational validation (by simulation or automated verification) with the real world employment of stand-alone solar PV systems. The final conclusion was that the proposed tool is sound and has an acceptable performance.

>>>>

In the houses that use a $975$ W PV system (house $1$, house $2$, house $3$, and house $4$), ESBMC reached an error in all the four houses and the execution time took less than $01$ s. Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for house $1$, with the FAIL identified. The authors highlighted the result, which shows that the design flaw was found (SAT result or SUCCESS) within the bound $k$ of $100$, when a PV panels total power of $1,636.76$ W is expected and the sized system has only $975$ W. This flaw is related to Eq.~\eqref{eq:Pminpanel}.

@@

\begin{figure}[h]
\fbox{\includegraphics[width=1.0\textwidth]{homersimuh2no.png}}
\centering
\caption{HOMER simulation screen presented for house 2 with no feasible solution found.}
\label{fig:homersimuh2no}
\end{figure}

@@

Further tests were performed in HOMER Pro. For example, to the case 1, that consumes $3.9$ kWh/day of energy: with the optimizer feature turned on, the total of PV panels minimum power expected to meet the load requirement was $2,530$ W. For the $3.6$ kWh/day of case 2, the PV panel solution indicated was $2,420$ W. For the $2.5$ kWh/day of case 3, the PV panel solution indicated was $1,590$ W. And, finally, for the $4.3$ kWh/day of case 4, the PV panel solution was $3,150$ W.

\begin{figure}[h]
\fbox{\includegraphics[width=1.0\textwidth]{homersimuh2yes.png}}
\centering
\caption{HOMER simulation screen presented for house 2 with viable solution.}
\label{fig:homersimuh2yes}
\end{figure}

@@

In order to evaluate the validation results, it was necessary to consult the interviews conducted with the residents of the $975$ W deployed systems. From July $2018$ to March $2019$, surveys were applied to the residents on a monthly basis and data was collected from a local monitoring system: energy interruptions of the PV systems were not reported every month and, in some, cases, the maximum of 3 interruptions were reported. In one hand, when only one interruption is reported per month, this represents around $3.33$\% interruption for the entire period ($1/30$), which indicates $96.97$\% of availability of the PV system ($96.67\% = 100\%-3.33\%$). In other hand, when 3 interruptions are reported\footnote{Crossed information from interviews and collected data from the systems shows that the residents try to hide (or minimize) the interruption problems of the PV systems. Probably because they need of the system and they try not to emphasize this issue}, this means $10$\% of interruption, or $90$\% of availability. In accordance to what was described in Section~\ref{sec:availability}, the type of electrical load of the houses is not critical. Therefore any availability below of $95$\% is a sizing flaw, further affirming EQ1. Moreover, the proposed approach using automated verification provides the correct evaluation of the PV system, as the simulation did, thus answering EQ2.

The automated verification tools indicated flaws in house $5$ as well; and was not possible to get HOMER Pro evaluation because of the autonomy restriction, further answering EQ2.

In order to validate the possible flaw identified by the automated verification in house $5$, the owner of the $1,300$ W system was interviewed. From this it became clear that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double-checked against the monitoring system of the charge controller, which showed that the maximum power or surge power was not exceeded. Even during the daylight, there is not enough energy produced by the solar PV panels to feed the loads, thus affirming EQ1; this behavior is to be expected since the system was purchased as an off-the-shelf solution and not as a customized design for the house's electrical charges.

@@

This Chapter presented a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
Nevertheless, it also identified six threats to the validity of the results that bear further assessment.

@@

\textit{Simulation tool:} Only HOMER Pro was used. The inclusion of other specialized simulation tools or even a general simulation tool that uses the same mathematical model adopted by the automated verification could change the comparison.

\textit{Temperature and solar irradiance data}: Information relating to the temperature and solar irradiance of each case study, whether it is using simulation or formal verification, comes from databases available online~\cite{Temperature, Irradiance}. However, in view of the fact that riverside communities do not have weather stations, the data used in the present study comes from the municipality closest (Manaus in all the case studies), where stations regularly collect the data. Nevertheless, accuracy recommends the use of weather stations in each location.

\textit{Energy consumption estimation}: All the PV size verification procedure start from the value of energy demanded from every house. However, this is a estimated value. Most recent information from field indicates that this value is overestimated and probably must be adjusted based on real data from a monitoring systems. The fact of the residents receive training to save energy is other issue that can reduce the total demanded energy from the PV systems. Therefore a most accurate validation can be performed when a real load curve is available for every case study.

@@

Based on the fact that all case studies were deployed in the field, with regular visits to conduct interviews with the residents (house $1$, house $2$, house $3$, and house $4$), it was possible to compare the computational validation (by simulation or automated verification) with the real world employment of stand-alone solar PV systems. Although residents report few monthly problems in homes that use a $975$ W solution, it is clear that in fact the interruption problem is much greater, as the original sized PV system is underestimated when it comes to power generation from solar panels and energy storage in batteries. The $1,300$ W system was classified as problematic by the owner, and our automated verification technique shows the design flaws. The final conclusion was that the proposed tool is sound and has an acceptable performance.
